Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-14 MS/ms.Rmd
Unified equations

eqns_yi <- c("M",
             "\\ln{SD} + \\frac{1}{2(N - 1)}",
             # Senior will have a better version but this is good for now
             "\\ln \\left( \\frac{M_{1}}{M_{2}}\\right)",
             "\\frac{\\left( X_{2} - X_{1}\\right)}{SD_{p}}J",
             # we need to spell out SD_p somewhere
             "\\frac{1}{2}log\\left(\\frac{1+r}{1-r}\\right)")
             #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
             #"- log\\left(\\frac{y_{i1}+0.5}{n_{i1}-y_{i1}+0.5}\\right)")

@@

$$
\begin{equation} 
  \begin{aligned}
  \ln{RR} = \ln\left ( \frac{X_{1}}{X_{2}}\right )
  \end{aligned}
  (\#eq:lnRR)
\end{equation} 
$$

$$
\begin{equation} 
  s^2_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
  (\#eq:slnRR)
\end{equation} 
$$ In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group). The mean of $X_{i}$ for group *i* can be any measurement type (e.g. a physiological rate, mass etc) so long as the measurement variable is ratio scale. Log transformation of this ratio makes the effect size normally distributed (most commonly assumed by meta-analytic models). Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.

>>>>

eqns_yi <- c("M",
             "\\ln{SD} + \\frac{1}{2(N - 1)}",
             # Senior will have a better version but this is good for now
             "\\ln \\left( \\frac{M_{1}}{M_{2}}\\right)",
             "\\frac{\\left( M_{2} - M_{1}\\right)}{SD_{p}}J",
             # we need to spell out SD_p somewhere
             "\\frac{1}{2}log\\left(\\frac{1+r}{1-r}\\right)")
             #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
             #"- log\\left(\\frac{y_{i1}+0.5}{n_{i1}-y_{i1}+0.5}\\right)")

@@

$$
\begin{equation} 
  \begin{aligned}
  \ln{RR} = \ln\left ( \frac{M_{1}}{M_{2}}\right )
  \end{aligned}
  (\#eq:lnRR)
\end{equation} 
$$

$$
\begin{equation} 
  s^2_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}M_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}M_{2}^2}\right )
  (\#eq:slnRR)
\end{equation} 
$$

In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group). The mean of $X_{i}$ for group *i* can be any measurement type (e.g. a physiological rate, mass etc) so long as the measurement variable is ratio scale. Log transformation of this ratio makes the effect size normally distributed (most commonly assumed by meta-analytic models). Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the sample variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
